Two-Phase Commit Using Blockchain

### 2022-06-04 paper/paper.tex
Updates paper.

We require the underlying database to be ACID because the database can handle locks and transactions natively without requiring cohorts to implement complicated locking logic for \texttt{Put} and \texttt{Get} operations. However, for databases that only support weak snapshot isolation (e.g. LMDB \cite{chu2020lightning}), the cohort needs a single write lock to prevent other write transactions to be started to make sure that transactions are serialized.

@@

While testing in the Truffle development, we learned the gas used for successfully committing a transaction with two cohorts is around 0.33 USD \cite{} (see \ref{appendix} for breakdowns).

>>>>

We require the underlying database to be ACID because the database can handle locks and transactions natively without requiring cohorts to implement complicated locking logic for \texttt{Put} and \texttt{Get} operations. However, for databases that only support weak snapshot isolation (e.g. LMDB \cite{henry2019howard}), the cohort needs a single write lock to prevent other write transactions to be started to make sure that transactions are serialized.

@@

While testing in the Truffle development, we learned the gas used for successfully committing a transaction with two cohorts is around 0.33 USD \cite{gwei} (see \ref{appendix} for breakdowns).
